Reaction & action alternatives

### 2023-05-30 01_studies/01_Laborstudie ProVisioNET/R script/action alternatives/reaction_action_alternatives.Rmd
Update reaction_action_alternatives.Rmd

# correlation: count x efficacy

>>>>

# correlation: count x quality 
```{r}

# filter for novices
main %>% 
  filter(id %in% c("Novice")) -> corr.nov

# filter for novices
main %>% 
  filter(id %in% c("Expert")) -> corr.exp

# novices: correlation between count and quality
cor.test(corr.nov$count, corr.nov$nd, method=c("spearman"))

# experts: correlation between count and quality
cor.test(corr.exp$count, corr.exp$nd, method=c("spearman"))

# correlation: reaction x count 
```{r}

# novices: correlation between reaction and count
cor.test(corr.nov$count, corr.nov$reaction, method=c("spearman"))

# experts: correlation between count and quality
cor.test(corr.exp$count, corr.exp$nd, method=c("spearman"))
